### 2011-02-03 docs/architecture/architecture.tex
updates to ghost cell fill stuff
minor fixes

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  MAESTRO can be built
with support for parallelism (using MPI or OpenMPI), or compiled
as a serial code.  The top portion
of the {\tt GNUmakefile} can be editted to choose the build options.
Setting {\tt MPI := t} will build the code to use MPI for parallelization.
Setting {\tt OMP := t} will use OpenMP.  If desired, these are used together,
with MPI distributing the grids across the processors and within a 
shared-memory node, OpenMP is used to allow many cores to operate
on the same grid.  A final build option determines whether to build
the code with support for debugging.  Setting {\tt NDEBUG := t} disables
debugging features.

Each problem will have one or more inputs files (for example, {\tt
  test2/inputs\_2d}) which override the default values for one or more
runtime parameters.  The code is run simply as:
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d
\end{verbatim}
As the code runs, it will output both plotfiles and checkpoints.
By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoints are named {\tt chk}{\em
  nnnnn}.  BoxLib plotfiles and checkpoints are actually directories,
with the data stored in subdirectories grouped by refinement level.
Details of the simulation (number of processors used, output date,
output directory, runtime parameter values, ...) are stored in
the {\tt job\_info} file in each plotfile directory.

@@

\item {\tt multifab\_fill\_ghost\_cells} is used for multilevel
  problems, and fills ghostcells in the finer grid (level {\tt n}) by
  interpolating from data in the coarser grid (level {\tt n-1}).

  This call is usually preceded by a call to {\tt
    ml\_cc\_restriction\_c} which sets the level {\tt n-1} data to be
  the average of the level {\tt n} data covering it.

>>>>

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  MAESTRO can be built
with support for parallelism (using MPI or MPI+OpenMP), or compiled
as a serial code.  The top portion
of the {\tt GNUmakefile} can be editted to choose the build options.
Setting {\tt MPI := t} will build the code to use MPI for parallelization.
Setting {\tt OMP := t} will use OpenMP.  OpenMP is used together with MPI, 
with MPI distributing the grids across the processors and within a 
shared-memory node, OpenMP allows many cores to operate
on the same grid.  A final build option determines whether to build
the code with support for debugging.  Setting {\tt NDEBUG := t} disables
debugging features.

Each problem will have one or more inputs files (for example, {\tt
  test2/inputs\_2d}) which override the default values for one or more
runtime parameters.  The code is run simply as:
\begin{verbatim}
  ./main.Linux.Intel.exe inputs_2d
\end{verbatim}
for a serial executable, and, depending on your MPI environment, something like:
\begin{verbatim}
  mpiexec -n 16 ./main.Linux.Intel.mpi.exe inputs_2d
\end{verbatim}
for the parallel code.

As the code runs, it will output both plotfiles and checkpoints.
By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoints are named {\tt chk}{\em
  nnnnn}.  BoxLib plotfiles and checkpoints are actually directories,
with the data stored in subdirectories grouped by refinement level.
Details of the simulation (number of processors used, output date,
output directory, runtime parameter values, ...) are stored in
the {\tt job\_info} file in each plotfile directory.

@@

\item {\tt multifab\_fill\_ghost\_cells} is used for multilevel
  problems, and fills ghostcells in the finer grid (level {\tt n}) by
  interpolating from data in the coarser grid (level {\tt n-1}).
  This function, by default, will also call {\tt multifab\_fill\_boundary}
  and {\tt multifab\_physbc} for both levels {\tt n} and {\tt n-1} (you 
  can override this behavior for speed optimization purposes).
  This call is usually preceded by a call to 
  {\tt ml\_cc\_restriction\_c} which sets the level {\tt n-1} data to be
  the average of the level {\tt n} data covering it.
